---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyGDPR)
```

# tidyGDPR

The General Data Protection Regulation (GDPR) as 'tidy' objects.

## Source

[http://openscience.adaptcentre.ie/projects/GDPRtEXT/](http://openscience.adaptcentre.ie/projects/GDPRtEXT/), made available under the [CC-by-4.0](https://creativecommons.org/licenses/by/4.0/) license.

## Installation

You can install the development version of tidyGDPR from [GitHub](https://github.com/jonocarroll/tidyGDPR) with:

```{r, eval = FALSE}
devtools::install_github("jonocarroll/tidyGDPR")
```

(please accept all cookies and agree to the terms and conditions.)

## Contents

`tidyGDPR` contains the recitals, chapters, and citations from the GDPR regulations as individual `tibble`s. The recitals

```{r GDPR_recitals}
GDPR_recitals
```

The chapters (articles, points, subpoints)

```{r GDPR_chapters}
GDPR_chapters
```

and the citations

```{r GDPR_citations}
GDPR_citations
```

Also included is the list of all these components, `GDPR_list`.

`GDPR_chapters` contains a column of `contents` which contains deeply nested `data.frame`s of articles, points, and subpoints. 

A helpful extractor function can extract articles and (any subset of) points from within chapters, by number

```{r extract}
# list all articles in chapter (1)
chapter_components(chapter = 1) 

# extract all points in (1, 1)
chapter_components(chapter = 1, article = 1) 

# extract (1, 1, 2)
chapter_components(chapter = 1, article = 1, points = 2) 
```

If you wish to obtain the full `GDPR_list` and these components yourself (in the case they are updated) `get_GDPR()` returns a list of each of the above data components.

## Future Work

- Ability to search the fulltext and return chapter/article/point/subpoint.
- ?
